NGO analysis

### 2022-08-02 Dashboard/NGO Analysis dashboard v006.Rmd
Cleaning up a comment.

  # Creating plotly output
  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot()) |>
      ## ggplot subtitles and captions are lost when using ggplotly(), a
      ## currency warning caption is therefore added in plotly, if needed, using
      ## a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )

>>>>

  # Creating plotly output
  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot()) |>
      # ggplot subtitles and captions are lost when using ggplotly(), a
      # currency warning caption is therefore added in plotly, if needed, using
      # a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )
